A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-12-04 draft/paper2_v9.tex
New edits from Alexie

\begin{abstract}

    To investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies, we use ${\sim}100$ deg$^2$ of 
    deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey.
    The $i$-band images from the HSC survey reach ${\sim}4$ magnitudes deeper than 
    Sloan Digital Sky Survey and enable us to directly trace stellar mass distributions 
    to 100 kpc without requiring stacking.  
    We conclusively show that, at fixed stellar mass, the stellar profiles of massive 
    galaxies depend on the masses of their dark matter haloes. 
    On average, massive central galaxies with \logmtot{}$>11.6$ in more massive haloes 
    at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
    (within ${\sim}10$--$20$ kpc) and more prominent outer envelopes. 
    These differences translate into a halo mass dependence of the 
    following mass--size relation: central galaxies in haloes with \logmh{}$>14.0$ are 
    $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}.  
    Such dependence is also reflected in the relationship between the stellar mass 
    within 10 and 100 kpc. 
    Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
    ambiguity in the definition of size, and can be straightforwardly compared with 
    simulations. 
    Our results demonstrate that, with deep images from HSC, we can quantify the 
    connection between halo mass and the outer stellar halo, which may provide new 
    constraints on the formation and assembly of massive central galaxies.

@@

    There have been multiple observational attempts to test the two-phase 
    formation scenario using galaxies at low redshift, by investigating surface 
    brightness or mass density profiles (e.g., \citealt{Huang2013a, Huang2013b, 
    Oh2017}, optical colour gradients (e.g., \citealt{LaBarbera2010, LaBarbera2012}), 
    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
    Greene2015, Barbosa2016}. 
    \song{
    These observations are generally consistent with the two-phase formation scenario. 
    However, it is still not clear whether this promising picture can correctly 
    predict the connection between the stellar mass distributions in massive galaxies 
    and their dark matter haloes.
    }

    \song{
    In the $\Lambda$CDM cosmology, the assembly of massive ETGs is intrinsically 
    tied to the hierarchical growth of their host dark matter haloes 
    (e.g., \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Hydrodynamic simulations suggest that the fraction of stars accreted through 
    mergers (\textit{ex situ} component) in a central galaxy increases with halo 
    mass (e.g., \citealt{RodriguezGomez2016, Pillepich2017b}). 
    The major merger rate is not a strong function of progenitor halo mass 
    (e.g., \citealt{Shankar2015}) but minor mergers can still play an important 
    role in determining the structures of central galaxies 
    (e.g., \citealt{Guo2011, Yoon2017}). 
    Minor mergers are efficient at `puffing up' the outskirts of massive 
    galaxies (e.g., \citealt{Oogi2013, Bedorf2013}). 
    Because the minor merger rate increases with halo mass, the 
    structures of massive ETGs and the well-known stellar mass--effective radius 
    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should 
    depend on their `environment'\footnote{There are multiple definitions of 
    `environment' in the literature. 
    In this work, we use `environment' and halo mass interchangeably.}
    (e.g., \citealt{Shankar2013, Shankar2014}). 
    However, evidence for the environment-dependence of \mstar{}--$R_{\rm e}$
    at low redshift is still not very solid (\citealt{Nair2010, HCompany13}; 
    but also see \citealt{Yoon2017}), and the results at higher redshift are 
    even more unclear (e.g., \citealt{Papovich2012, Lani2013, Delaye2014}; but 
    also see \citealt{Rettura2010}).
    }

	\song{
    Deep images of massive galaxies can probe the outer stellar halos of massive 
    galaxies and test these predictions. 
    Unfortunately, this is observationally challenging since the stellar haloes 
    of massive galaxies can extend to $>100$ kpc (e.g., 
    \citealt{Tal2011, DSouza2014}), and their surface brightness profiles decline 
    rapidly with typical values of $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and 
    at $z\sim0.3$. 
    }
    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
    multi-band imaging from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} galaxies with 
    \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
    In Paper I, we characterized the stellar mass profiles of massive ETGs and 
    showed that there is a large intrinsic scatter in the \mden{} stellar haloes of
    massive galaxies on 100-kpc scales. 
    In this paper, we investigate whether the large scatter in the outer 
    profiles of massive galaxies correlates with halo mass. 
    We conclusively show that the sizes and stellar haloes of massive central galaxies 
    depend on dark matter halo mass. 
    In other words, we reveal the halo mass dependence of the mass--size relation 
    for massive ETGs.

@@

    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
    redshifts or reliable `red-sequence' photometric redshifts (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. 
    Within this redshift range, we have a large enough volume 
    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
    \logms$>11.6$, and we can spatially resolve galaxies profiles to $\sim 5$ kpc 
    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5). 
    \song{
    Massive galaxies should experience little structural evolution and 
    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr time span) 
    based on model prediction (e.g., \citealt{Shankar2015}).
    }

@@

        \item Stellar mass within 10 kpc (hereafter noted \minn{}), which we use 
            as a proxy for the stellar mass of the \textit{in situ} stellar 
            component. 
            This is motivated both by recent observations and simulations 
            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). 
            The value of 10 kpc that we quote here corresponds to the radius of the 
            major axis of the isophotal ellipse.

        \item Stellar mass within 100 kpc (hereafter noted \mtot{}). 
            We use \mtot{} as a proxy for the `total' stellar mass. 
            In Paper~I we show that \mtot{} recovers more light compared to 
            HSC \cmodel{} photometry and has offsets that can be a large as 0.2 dex 
            in magnitude.

@@

   We use these two simple metric masses to explore the \mstar{}-dependence of the 
   fraction of accreted stars and to reveal the diversity of stellar envelopes among 
   massive galaxies. 
   In practice, we also have the full profiles for each galaxy and can cast our 
   results in terms of the full stellar mass profiles. 
   However, in many cases we find it more useful to display figures using the simpler 
   \minn{} and \mtot{} quantities. 
   In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
   function of \minn{} and \mtot{}. 
   Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with 
   very similar \minn{} that have a large range of \mtot{}. 
   We use these two aperture masses to guide our comparison of massive galaxies 
   as a function of environment.

@@

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that this sample is almost mass complete over our full 
    redshift range. 
    In addition to the mass cut above, we also limit our sample to galaxies that live 
    at the centers of their own dark matter haloes -- so-called `central' galaxies. 
    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
    to help us construct a central galaxy sample.

@@

    First, we select 68 massive central galaxies from \redm{} clusters 
    with richness $\lambda \geq 30$, and we assign the probability of true central 
    galaxy $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$ >11.5$ 
    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$ >11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalogue
    at the high end of our redshift window. 
    The $P_{\mathrm{Cen}}$ limit is selected to exclude low-probability candidates for 
    central galaxy. 
    \song{
    \citet{Simet2017} calibrates the \mhalo{}-$\lambda$ relation for the \redm{} 
    clusters using the SDSS weak-lensing data after carefully addressing many 
    important systematic uncertainties.
    Based on this calibration, these clusters correspond to central galaxies living 
    in haloes with \mhalo{}$>10^{14.2}$~\msun{}. 
    This calibration is consistent with several other independent calibrations 
    using different methods (e.g., \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    }
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
    only 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We refer to this sample of \textbf{central galaxies in massive haloes} as 
    the \rbcg{} sample.

    Second, we build a complementary sample of central galaxies in lower mass haloes
    by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
    \song{
    We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
    \citet{Simet2017}. Using the \texttt{Colossus} Python package 
    (\citealt{Colossus})\footnote{\url{http://www.benediktdiemer.com/code/colossus/}}
    provided by \citet{Diemer2015}, we estimate the $R_{\mathrm{200b}}$ of each 
    cluster given its $M_{\mathrm{200b}}$ and redshift.
    } 
    We exclude all galaxies within a cylinder around each cluster, with a radius
    equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the 
    photometric redshift uncertainty of the cluster (typically around 0.015 to 0.025).
    This second sample is dominated by central galaxies living in haloes with
    $M_{\mathrm{200b}} < 10^{14}$~\msun{}; we refer to this sample as \nbcg{}. \
    There are 833 central galaxies with \logmtot{}$> 11.6$ in this sample.

    Satellite contamination should be relative low at the high-\mtot{} end
    (e.g., \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
    For instance, the model from \citet{Saito2016} predicts a $\sim 7$\% 
    fraction for satellite galaxies with \logmtot{}$>11.6$ and \logmh$<14.0$ haloes.

    In Appendix~\ref{app:basic}, we show the distributions of redshift, \mtot{}, and 
    \minn{} for the \rbcg{} and \nbcg{} samples. 
    We also compare these two samples on a \mtot{} versus rest--frame $(g-r)$ colour 
    plane. 
    Both of the samples follow the same red-sequence, with only a handful of galaxies 
    displaying bluer colours.

    We note that our analysis fails to extract 1-D profiles for $\sim10$\% of 
    \rbcg{} and \nbcg{} galaxies due to ongoing major mergers or projection effects 
    (e.g.\ nearby foreground galaxy or bright stars). 
    However, this small failure rate should not affect any of the results in this paper.

@@

    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies at fixed  
    \minn{} display a large diversity in their stellar haloes. 
    In Paper~I, we explore the \mstar{}-dependence of the stellar haloes in massive 
    galaxies, we now investigate the relation between the \mden{} profiles of 
    massive galaxies, their stellar haloes, and dark matter halo mass. 
    %Here we use \mtot{} as a proxy for the `total' \mstar{} of massive galaxies, and 
    %we use \minn{} as a rough proxy for the stellar mass of the \textit{in situ} 
    %component.  
    We remind the reader that although a circular aperture is shown on 
    Fig~\ref{fig:m100_m10_color}, in practice we extract 1-D \mden{} profiles and 
    estimate \mtot{} and \minn{} using elliptical apertures following the average 
    flux-weighted isophotal shape.

@@

    First, we ask whether the \mden{} profiles of massive central galaxies depend on 
    halo mass at a fixed stellar mass.    
    We show comparisons of \mden{} profiles at both fixed \mtot{} and fixed 
    \minn{}. 
    We also ensure that all comparisons are performed with a fixed underlying redshift
    distribution by matching samples in redshift in addition to a fixed stellar mass
    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
    and Fig~\ref{fig:match} for details).

%% ------------------------------------------------------------------------------------ %%     
    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies 
    living in less massive dark matter haloes (\logmh$<14.0$) to those living in more 
    massive dark matter haloes (\logmh$>14.2$) at fixed \mtot{} (left panel) and at 
    fixed \minn{} (right panel). 
    At fixed \mtot{}, we compare massive galaxies that have similar `total' \mstar{}. 
    On the right side, we use \minn{} as a proxy for the \textit{in situ} \mstar{} to 
    compare the overall \mstar{} distributions of galaxies living in different 
    environments that have assembled a similar amount of stars at high-$z$.
    This figure shows the main result of this paper, namely that 
    \emph{the \mden{} profiles of massive central galaxies show a clear dependence on 
    dark matter halo mass at both fixed \mtot{} and \minn{}.}

    \song{
    We estimate the uncertainties of the median \mden{} profiles using a bootstrap 
    resampling test, and we perform statistical tests to demonstrate that the 
    differences of \mden{} profiles are more significant than the levels allowed by 
    the intrinsic randomness within the combined \rbcg{} and \nbcg{} sample. 
    }
    We also conduct a variety of tests that verify the robustness of these results with
    respect to the choices of \mtot{} bins, $\lambda$ cut, the redshift range, and the 
    choice of apertures used for the metric masses. 
    Please see Appendix~\ref{app:robust} for further details.
    \song{
    In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we compare the same 
    \mtot{}-matched samples using the cumulative \mstar{} profiles (or `curve of growth') 
    and the fraction of \mtot{} enclosed within different radii.
    Both comparisons highlight the differences in median \mden{} profiles 
    from different angles.   
    }

@@

        \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
            display shallower \mden{} profiles compared to those from less massive 
            dark matter haloes (i.e., they have flatter inner \mden{} profiles and 
            more significant outer stellar haloes). 
            The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
            ($R_{\mathrm{e}}$) of massive galaxies with \logmtot{}$>11.7$--11.8.

        \item \song{
            For the \mtot{}-matched samples, there are some subtle but statistically 
            significant and robust differences between the two median \mden{} profiles.
            Due to the logarithmic scale, the difference in the inner region appears 
            to be very small. 
            Meanwhile, the difference in the \mden{} profile becomes more apparent 
            at $R>50$ kpc scales.  
            }

        \item Massive galaxies with similar \mstar{} within 10 kpc have quite
            different \mtot{} and massive central galaxies in more massive haloes 
            host much more prominent outer stellar haloes.

        \item The similar slopes of the \mden{} profiles within 10 kpc for the 
            \minn{}-matched samples are in sharp contrast with the large 
            \textit{intrinsic} scatter we see in the outer \mden{} profiles. 
            We will discuss the inner \mden{} profiles further in \S~\ref{ssec:cen}

    \song{
    Fig \ref{fig:prof_1} shows that the environmental dependence of the profiles of m
    assive central galaxies is a subtle effect.
    }
    This may explain why previous attempts to detect such dependence using 
    shallower images often failed. In Appendix~\ref{app:robust} (see Fig~\ref{fig:prof_2}) 
    we demonstrate that the environmental signature becomes more prominent for more massive 
    galaxies.

    \textbf{In summary, we reliably detect a subtle, but robust halo mass dependence of 
    the profiles of massive central galaxies. 
    This dependence could be driven by the fact that massive halos have a larger minor 
    merger rate compared to less massive haloes. 
    Nondissipative (minor) mergers should not strongly alter the inner \mden{} 
    profiles, but can efficiently build up the outer halo 
    (e.g., \citealt{Hilz2013}, \citealt{Oogi2013})}.

@@

    We have shown that the \mden{} profiles of massive galaxies 
    show a dependence on the masses of their host dark matter haloes. 
    In this section, we turn our attention to the more commonly studied stellar 
    mass--size relation (\mstar{}--$R_{\mathrm{e}}$). 
    In addition, we consider halo mass dependence on the 
    \mtot{}--\minn{} plane.

@@

    \song{
    We emphasize the fact that `size' is not a well-defined parameter for massive 
    galaxies with very extended stellar mass distributions. 
    In practice, the measurements of `effective radius' or `half-light radius' 
    not only depend on resolution, depth, and filter of the image, but may also 
    depend on the adopted model for the light profile.  
    This makes comparisons of size measurements among different observations 
    or between observations and models much more uncertain, and is the main reason
    why we prefer to compare the \mden{} profiles directly.
    }
    In this section, we adopt the radius enclosing 50\% of stellar mass within 
    100 kpc ($R_{\mathrm{50}}$; derived from the $i$-band curve-of-growth) as the 
    `size' for massive galaxies. 
    Such a definition of `half-light radius' is more robust against structural 
    details, choice of model, and the background subtraction compared to the 
    effective radius measured using a 2-D model with oversimplified assumptions 
    (e.g., single-\ser{} model). 
    Massive galaxies in this sample are large enough so that the impact of seeing 
    is not a concern.

>>>>

\begin{abstract}  We use ${\sim}100$ deg$^2$ of 
    deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey to reveal the halo mass dependence of the surface mass density profiles and outer stellar envelopes of massive galaxies. The $i$-band images from the HSC survey reach ${\sim}4$ magnitudes deeper than 
    Sloan Digital Sky Survey and enable us to directly trace stellar mass distributions 
    to 100 kpc without requiring stacking.  
    We conclusively show that, at fixed stellar mass, the stellar profiles of massive 
    galaxies depend on the masses of their dark matter haloes. 
    On average, massive central galaxies with \logmtot{}$>11.6$ in more massive haloes 
    at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
    (within ${\sim}10$--$20$ kpc) and more prominent outer envelopes. 
    These differences translate into a halo mass dependence of the mass--size relation. Central galaxies in haloes with \logmh{}$>14.0$ are $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}. Such dependence is also reflected in the relationship between the stellar mass 
    within 10 and 100 kpc.  Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
    ambiguity in the definition of size, and can be straightforwardly compared with 
    simulations. 
    Our results demonstrate that, with deep images from HSC, we can quantify the 
    connection between halo mass and the outer stellar halo, which may provide new 
    constraints on the formation and assembly of massive central galaxies.

@@

    There have been multiple observational attempts to test the two-phase 
    formation scenario using galaxies at low redshift, by investigating surface 
    brightness or mass density profiles (e.g., \citealt{Huang2013a, Huang2013b, 
    Oh2017}, optical colour gradients (e.g., \citealt{LaBarbera2010, LaBarbera2012}), 
    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
    Greene2015, Barbosa2016}. 
    \song{
    These observations are generally consistent with the two-phase formation scenario. 
    However, it is still not clear whether this picture correctly 
    predicts the connection between the stellar mass distributions in massive galaxies 
    and their dark matter haloes.}

     \song{In the $\Lambda$CDM cosmology, the assembly of massive ETGs is intrinsically 
    tied to the hierarchical growth of their host dark matter haloes 
    (e.g., \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Hydrodynamic simulations suggest that the fraction of stars accreted through 
    mergers (the \textit{ex situ} component) in central galaxies increases with halo 
    mass (e.g., \citealt{RodriguezGomez2016, Pillepich2017b}). 
    The major merger rate is not a strong function of progenitor halo mass 
    (e.g., \citealt{Shankar2015}) but minor mergers can still play an important 
    role in determining the structures of central galaxies 
    (e.g., \citealt{Guo2011, Yoon2017}). 
    Minor mergers are efficient at `puffing up' the outskirts of massive 
    galaxies (e.g., \citealt{Oogi2013, Bedorf2013}). 
    Because the minor merger rate increases with halo mass, the 
    structures of massive ETGs and the well-known stellar mass--effective radius 
    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should 
    depend on their `environment'\footnote{There are multiple definitions of 
    `environment' in the literature. 
    In this work, we use `environment' and halo mass interchangeably.}
    (e.g., \citealt{Shankar2013, Shankar2014}). 
    However, evidence for the environment-dependence of \mstar{}--$R_{\rm e}$
    at low redshift is still not very solid (\citealt{Nair2010, HCompany13}; 
    but also see \citealt{Yoon2017}), and the results at higher redshift are 
    even more unclear (e.g., \citealt{Papovich2012, Lani2013, Delaye2014}; but 
    also see \citealt{Rettura2010}).
    }

	\song{
    Deep images of massive galaxies can probe the outer stellar halos of massive 
    galaxies and test these predictions. 
    Unfortunately, this is observationally challenging since the stellar haloes 
    of massive galaxies can extend to $>100$ kpc (e.g., 
    \citealt{Tal2011, DSouza2014}), and their surface brightness profiles decline 
    rapidly with typical values of $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and 
    at $z\sim0.3$. 
    }
    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
    multi-band imaging from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} galaxies with 
    \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
    In Paper I, we characterized the stellar mass profiles of massive ETGs and 
    showed that there is a large intrinsic scatter in the stellar haloes of
    massive galaxies on 100-kpc scales. 
    In this paper, we investigate whether the large scatter in the outer 
    profiles of massive galaxies correlates with halo mass. 
    We conclusively show that the sizes and stellar haloes of massive central galaxies 
    depend on dark matter halo mass. 
    In other words, we reveal the halo mass dependence of the mass--size relation 
    for massive ETGs.

@@

    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
    redshifts or reliable `red-sequence' photometric redshifts (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. 
    Within this redshift range, we have a large enough volume 
    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
    \logms$>11.6$, and we can spatially resolve galaxies profiles to $\sim 5$ kpc 
    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5). 
    \song{
    Massive galaxies should experience little structural evolution and 
    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr time span) 
    based on model predictions (e.g., \citealt{Shankar2015}).
    }

@@

        \item Stellar mass within 10 kpc (hereafter noted \minn{}), which we use 
            as a proxy for the stellar mass of the \textit{in situ} stellar 
            component. 
            This is motivated both by observations and simulations 
            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). 
            The value of 10 kpc that we quote here corresponds to the radius of the 
            major axis of the isophotal ellipse.

        \item Stellar mass within 100 kpc (hereafter noted \mtot{}). 
            We use \mtot{} as a proxy for the `total' stellar mass. 
            In Paper~I we show that \mtot{} recovers more light compared to 
            HSC \cmodel{} photometry with differences that can be a large as 0.2 dex 
            in magnitude.

@@

   We use these two simple metric masses to explore the \mstar{}-dependence of the 
   fraction of accreted stars and to reveal the diversity of stellar envelopes among 
   massive galaxies. 
   In practice, we also have the full profiles for each galaxy and can cast our 
   results in terms of the full stellar mass profiles. 
   However, in many cases we find it useful to display figures using the simpler 
   \minn{} and \mtot{} quantities. 
   In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
   function of \minn{} and \mtot{}. 
   Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with 
   very similar \minn{} that have a large range of \mtot{}. 
   We use these two aperture masses to guide our comparison of massive galaxies 
   as a function of environment.

@@

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that this sample is almost mass complete over our full 
    redshift range. 
    In addition to the mass cut above, we also limit our sample to galaxies that live 
    at the centers of their own dark matter haloes -- so-called `central' galaxies. 
    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
    to help us construct two central galaxy samples.

@@

    First, we build a sample of central galaxies in high mass haloes. We select 68 massive central galaxies from \redm{} clusters 
    with richness $\lambda \geq 30$, with central probability $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$ >11.5$ 
    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$ >11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalogue
    at the high end of our redshift window. 
    The $P_{\mathrm{Cen}}$ limit is imposed to limit our sample to central galaxies. 
    \song{
    \citet{Simet2017} present a calibration of the \mhalo{}-$\lambda$ relation for \redm{} 
    clusters using SDSS weak-lensing. Based on this calibration, our sample corresponds to central galaxies living 
    in haloes with \mhalo{}$>10^{14.2}$~\msun{}. 
    This calibration is consistent with several other independent calibrations 
    using different methods (e.g., \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    }
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We refer to this sample of \textbf{central galaxies in massive haloes} as 
    the \rbcg{} sample.

    Second, we build a sample of central galaxies in low mass haloes. We begin by excluding all galaxies in \redm{} clusters with $\lambda > 20$.
    \song{
    We convert $\lambda$ to $M_{\mathrm{200b}}$ using the \citet{Simet2017} calibration. For each cluster, we compute $R_{\mathrm{200b}}$ using the \texttt{Colossus} Python package 
    (\citealt{Colossus})\footnote{\url{http://www.benediktdiemer.com/code/colossus/}}
    provided by \citet{Diemer2015}} 
    We exclude all galaxies within a cylinder around each cluster, with a radius
    equal to $R_{\mathrm{200b}}$, and a length equal to twice the value of the 
    photometric redshift uncertainty of the cluster (typically around 0.015 to 0.025).
    This second sample is dominated by central galaxies living in haloes with
    $M_{\mathrm{200b}} < 10^{14}$~\msun{}; we refer to this sample as \nbcg{}. \
    There are 833 central galaxies with \logmtot{}$> 11.6$ in this sample.

    Satellite contamination in our sample should be low (e.g., \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
    For instance, the model from \citet{Saito2016} predicts that our \rbcg{} sample should only contain $\sim 7$\% satellites (corresponding to satellites with \logmtot{}$>11.6$ and living in haloes with \logmh$<14.0$).

    Appendix~\ref{app:basic} shows the distributions of redshift, \mtot{}, and 
    \minn{} for the two samples. 
    We also compare these two samples on a \mtot{} versus rest--frame $(g-r)$ colour 
    plane. 
    Both samples follow the same red-sequence, with only a handful of galaxies 
    displaying bluer colours.

    Our analysis fails to extract 1-D profiles for $\sim10$\% of 
    \rbcg{} and \nbcg{} galaxies due to ongoing major mergers or projection effects 
    (e.g.\ nearby foreground galaxy or bright stars). 
    However, this small failure rate should not affect any of our results.

@@

    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies at fixed  
    \minn{} display a large diversity in their stellar haloes. 
    In Paper~I, we explored the \mstar{}-dependence of these stellar haloes. We now investigate the relation between \mden{} profiles, stellar haloes, and dark matter halo mass. We remind the reader that although a circular aperture is shown on 
    Fig~\ref{fig:m100_m10_color}, in practice we extract 1-D \mden{} profiles and 
    estimate \mtot{} and \minn{} using elliptical apertures following the average 
    flux-weighted isophotal shape.

@@

    First, we ask whether the \mden{} profiles of massive central galaxies depend on 
    halo mass at fixed stellar mass.    
    We show comparisons of \mden{} profiles at both fixed \mtot{} and fixed 
    \minn{}. All comparisons are performed with a fixed underlying redshift
    distribution by matching samples in redshift in addition to stellar mass
    (see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
    and Fig~\ref{fig:match} for details).

%% ------------------------------------------------------------------------------------ %%     
    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies in low mass haloes to those in high mass haloes at fixed \mtot{} (left panel) and at fixed \minn{} (right panel). The left panel compares galaxies that have similar `total' stellar mass. The right panel uses \minn{} as a proxy for the \textit{in situ} component to 
    compare the profiles of galaxies that presumably have similar early formation histories, but which live in different dark matter haloes today. This figure shows the main result of this paper, namely that 
    \emph{the \mden{} profiles of massive central galaxies show a clear dependence on 
    dark matter halo mass at both fixed \mtot{} and \minn{}.}

    \song{
    We estimate the uncertainties of the median \mden{} profiles using a bootstrap 
    resampling test, and we perform statistical tests to demonstrate that the 
    difference between the profiles is more significant than the level allowed by 
    the intrinsic randomness within the combined \rbcg{} and \nbcg{} sample. 
    }
    We also conduct a variety of tests that verify the robustness of these results with
    respect to our \mtot{} binning scheme, $\lambda$ cut, the redshift range, and the 
    choice of apertures used for the metric masses. 
    Please see Appendix~\ref{app:robust} for further details.
    \song{Appendix \ref{app:cog} and Figure~\ref{fig:cog} compares the same 
    \mtot{}-matched samples using cumulative \mstar{} profiles (`curve of growth') 
    and the fraction of \mtot{} enclosed within different radii.
    Both comparisons highlight the differences in the median \mden{} profiles 
    from different angles.   
    }

@@

        \item At fixed \mtot{}, central galaxies in high mass haloes 
            display shallower \mden{} profiles compared to those in low mass haloes (i.e., they have flatter inner \mden{} profiles and 
            more significant outer stellar envelopes).

            \item  The median \mden{} profiles of the two samples cross 
            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
            ($R_{\mathrm{e}}$) of galaxies at these masses (\logmtot{}$>11.7$--11.8).

            \item \song{
            When matched by \mtot{}, differences in the inner regions appear 
            to be small, but this is also driven by the use of a logarithmic y-axis. The difference becomes more apparent 
            at $R>50$ kpc.  
            }

        \item Massive galaxies matched by \minn{} display a range of  \mtot{} values. Those in massive dark matter halos have more prominent outer stellar haloes. The scatter in the outer profiles observed in Figure \ref{fig:prof_1} is an \textit{intrinsic} scatter (not measurement error).                     
    \end{itemize}

    \song{
    Fig \ref{fig:prof_1} shows that the environmental dependence of the profiles of massive central galaxies is a subtle effect that is most prominent at large radii ($R>50$ kpc).
    } This may explain why previous attempts to detect this effect using 
    shallower images have often failed.

    The effect becomes more pronounced for even more massive galaxies. This is shown in Fig~\ref{fig:prof_2} in Appendix~\ref{app:robust}.

    In summary, we detect a subtle, but robust halo mass dependence of 
    the profiles of massive central galaxies. 
    This dependence could be driven by the fact that massive halos have a larger minor 
    merger rate compared to less massive haloes. 
    Nondissipative (minor) mergers should not strongly alter inner 
    profiles, but can efficiently build up outer haloes 
    (e.g., \citealt{Hilz2013}, \citealt{Oogi2013}).

@@

    We have shown that the \mden{} profiles of massive galaxies vary with the masses of their host dark matter haloes. We now turn our attention to the more commonly studied stellar 
    mass--size relation (\mstar{}--$R_{\mathrm{e}}$). 
    In addition, we consider halo mass dependence on the 
    \mtot{}--\minn{} plane.

@@

    \song{However, `size' is not a well-defined parameter for massive 
    galaxies with very extended stellar mass distributions. 
    In practice, measurements of the `effective radius', or `half-light radius', depend on resolution, depth, filter, and may also 
    depend on the adopted model for the light profile.  
    This makes comparisons of size measurements among different observations, 
    or between observations and models, uncertain. This is the main reason
    why we prefer to compare \mden{} profiles directly which completely bypasses the need to consider `size'.
    }

    Nonetheless, to enable comparisons with past work, we now consider the more traditional mass-size relation. We adopt the radius enclosing 50\% of stellar mass within 
    100 kpc ($R_{\mathrm{50}}$; derived from the $i$-band curve-of-growth) as our 
    `size' for massive galaxies. This definition of `half-light radius' is more robust against structural 
    details, model choice, and background subtraction, compared to the 
    effective radius measured using oversimplified 2-D models such as the single-\ser{} model. 
    Massive galaxies in this sample are large enough so that the impact of seeing 
    is not a concern.

    The left panel of Fig~\ref{fig:scaling_relation} shows the mass-size relation for our two samples. We fit the \logmtot{}-$\log_{10} (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
    $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
    (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
    likelihood estimates, and we assume flat priors for parameters.}.
    \song{
    Uncertainties in both \mtot{} and $R_{\mathrm{50}}$ are considered. 
    For \logmtot{}$>11.6$ galaxies, the typical uncertainty for mass is $\sim 0.12$
    dex.  
    The $R_{\mathrm{50}}$ uncertainty is based on the \mden{} profile and
    is very small due to the high \s2n{} of the profile. 
    We manually assign a 10\% error for $R_{\mathrm{50}}$. 
    }
